Redshift evolution of the underlying type Ia supernova stretch distribution

### 2021-03-05 Nicolas.tex
Not inversing 'are used' and 'are compared' in fine

\date{Submitted to A\&A the 19th of May 2020}

@@

We note that when models that were adjusted on individual subsamples rather than
globally \textbf{are compared}, the Bayesian information criterion
($\mathrm{BIC} = -2\ln(L) + k\ln(n)$, with $n$ the number of data points) might
be better suited than AIC because it explicitly accounts for the fact that each
subsample is fitted separately: the sample-based model BIC is rightfully the sum
of the BIC for each sample. We find $\Delta\mathrm{BIC}=-48$, again refuting the
sample-based asymmetric Gaussian model as being as pertinent as the base model.

@@

In the era of modern cosmology, where we aim to measure $w_0$ at a subpercent
level and $w_a$ with 10\%\ precision \citep[e.g.,][]{lsstpaper}, we stress that
correct modeling of potential SN redshift drift should be further studied and
care should be taken when samples that are affected by observational selection
effects are used.

>>>>

\date{Submitted to A\&A\ the 19th of May 2020}

@@

We note that when models are compared that were adjusted on individual
subsamples rather than globally, the Bayesian information criterion
($\mathrm{BIC} = -2\ln(L) + k\ln(n)$, with $n$ the number of data points) might
be better suited than AIC because it explicitly accounts for the fact that each
subsample is fitted separately: the sample-based model BIC is rightfully the sum
of the BIC for each sample. We find $\Delta\mathrm{BIC}=-48$, again refuting the
sample-based asymmetric Gaussian model as being as pertinent as the base model.

@@

In the era of modern cosmology, where we aim to measure $w_0$ at a subpercent
level and $w_a$ with 10\%\ precision \citep[e.g.,][]{lsstpaper}, we stress that
correct modeling of potential SN redshift drift should be further studied and
care should be taken when samples are used that are affected by observational
selection effects.
